Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-23 introduction.tex
Removed unnecessary variable (t)
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1149 ccdd05d5-56c1-461a-bf98-85f6876523b4

\begin{figure}[h]
\plotone{figures/snr_in_time.pdf}
\caption{\label{fig:earlywarning}Expected number of \textsc{ns}--\textsc{ns}
sources that will be detectable by Advanced \LIGO\ $t$ seconds before coalescence.
The heavy solid line is the most realistic yearly rate estimate.  The shaded
region represents the 5 to 95\% confidence interval arising from uncertainty
in predicted event rates \citep{Abadie:2010p10836}.}
\end{figure}
%
It has been observed that by examining the signal to noise ratio (\SNR{}) stream for
threshold crossings before the \GW{} signal leaves the detection band, it is
possible to trade some \SNR{} and sky localization accuracy for pre-merger
detection. Figure~\ref{fig:earlywarning} shows projected early detection rates
for \textsc{ns}--\textsc{ns} binaries in Advanced \LIGO\ assuming event rates
predicted in \citet{Abadie:2010p10836} and anticipated detector sensitivity for
the `zero detuning, high power' configuration described in \citet{ALIGONoise}.
The most realistic estimates indicate that at an \SNR\ threshold of 8, we will
observe a total of 40~events~yr$^{-1}$, but $\sim$10~yr$^{-1}$ will be
detectable within 10~s of merger and $\sim$5~yr$^{-1}$ will be detectable
within 25~s of merger. These rates are shown with their substantial uncertainties in figure~\ref{fig:earlywarning}.

>>>>

\begin{figure}[h]
\plotone{figures/snr_in_time.pdf}
\caption{\label{fig:earlywarning}Expected number of \textsc{ns}--\textsc{ns}
sources that will be detectable by Advanced \LIGO\ a given number of seconds before coalescence.
The heavy solid line is the most realistic yearly rate estimate.  The shaded
region represents the 5 to 95\% confidence interval arising from uncertainty
in predicted event rates \citep{Abadie:2010p10836}.}
\end{figure}
%
It has been observed that by examining the signal to noise ratio (\SNR{}) stream for
threshold crossings before the \GW{} signal leaves the detection band, it is
possible to trade some \SNR{} and sky localization accuracy for pre-merger
detection. Figure~\ref{fig:earlywarning} shows projected early detection rates
for \textsc{ns}--\textsc{ns} binaries in Advanced \LIGO\ assuming event rates
predicted in \citet{Abadie:2010p10836} and anticipated detector sensitivity for
the `zero detuning, high power' configuration described in \citet{ALIGONoise}.
The most realistic estimates indicate that at an \SNR\ threshold of 8, we will
observe a total of 40~events~yr$^{-1}$, but $\sim$10~yr$^{-1}$ will be
detectable within 10~s of merger and $\sim$5~yr$^{-1}$ will be detectable
within 25~s of merger. These rates are shown with their substantial uncertainties in figure~\ref{fig:earlywarning}.
